Modelling BCG vaccination in the UK

### 2019-06-17 rmds/03-getTBinR.Rmd
updated getTBinR install instructions

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount: 1796
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR")
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```

>>>>

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount: 1796
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR", update = TRUE)
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```
